\textbf{\sc Towards Deliberative Control of Autonomous Robots}

### 2012-02-06 trunk/europa-basics.tex
updates

Constraint Satisfaction Programming (also known as Constraint
Programming (CP)) is a discipline that provides a generic framework for
representing, solving and making logical inference on constraints. A
complete treatment of this discipline is given in [MAR98] and [APT03]
and very concise introductions are provided in [BAR99] and
[LUS01].\comment{fix citations}

@@

CP is normally implemented as part of a programming language and
constraints are normally represented as objects [PUG95]
\comment{citation}. Any constraint can be introduced and, as long as the
bounds propagation and domain reduction protocols specified by the host
CP system are enforced, it will be indistinguishable from any other
``primitive'' CP constraint, such as $\leq$ or $\geq$. In theory,
solving a CSP problem is NP-Hard \cite{ghallab04}, but often very
efficient in practice using a number of algorithms and techniques that
are well understood.

@@

    An object is an instance of a class. In EUROPA we model using the
    abstraction of a class to speak about all instances having certain
    properties of state and behavior. In order to describe such state
    and behavior we build on the formalism of first order logic.

@@

A predicate defines a relation between objects and properties. In
EUROPA, we define such relations between variables whose domains are
sets of objects and sets of properties. For example, we might use a
predicate Pointing(a,p) to indicate that a rover's attitude controller
a is pointing at position p. Note that a is a variable which may have
a number of possible values in a problem with multiple
satellites. Similarly, p is a variable whose values are the set of
possible positions. In a grounded plan, single values will be
specified for each variable as we saw in the case of a solved
Constraint Satisfaction Problem.

In general, is is not sufficient to state that a predicate is true
without giving it some temporal extent over which it holds. Predicates
that are always true can be thought to hold from the beginning to the
end of time. However, in practice, the temporal extent of interest
must be defined with timepoints to represent its start and end. So we
might want to write Pointing(a,s,e,p) to indicate that the attitude
controller a is pointing at position p from time s to time e. In fact,
this pattern of using such predicates to describe both state and
behavior of objects is so prevalent in EUROPA that we have introduced
a special construct called a Token which has the built in variables to
indicate the object to which the statement principally applies and the
timepoints over which it holds. In EUROPA, all predicate instances are
Tokens.

@@

Timelines: Often objects in a domain must be described by exactly one
token for every given timepoint in the plan. Such objects are so
common that we provide a special construct in EUROPA to extend these
semantics to derived classes. Any instances of a class derived from a
Timeline will induce ordering requirements among its tokens in order
to ensure no temporal overlap may occur among them. See below for
further discussion.

Resources: Metric resources, e.g. the energy of a battery or the
capacity of a cargo hold, are objects with an explicit quantitative
state in time and with a circumscribed range of changes that can occur
to impact that state i.e. produce, consume, use, change. These changes
are captured as tokens. Resources are such a common requirement for
EUROPA users that special constructs are also provided for
them. Instances of classes derived from a Resource will induce
ordering requirements on their Tokens in order to ensure that the
level of the resource remains within specified limits.

@@

It may be sufficient to maintain only a partial-order among
tokens. However, it is often the case that tokens represent states and
actions of a single object in the system. Such tokens are typically
mutually-exclusive. EUROPA uses a Timeline structure developed in (??)
to concisely capture system components whose behavior is described
over time in this manner.

@@

Figure 1 illustrates how a Timeline can be used to describe the
whereabouts of a tire. The tire is an object in the tire-world
represented as a timeline. It has predicates associated with it which
can describe its states and actions over time. The predicate names
need not contain the tire prefix; this is now implicit since the
tokens are assigned to a specific tire instance (i.e. an instance of a
Timeline). While Timelines are a useful element of the EUROPA planning
paradigm, they are not essential. A more general notion of a system
Object can be used which does not impose restrictions of
mutual-exclusion or non-zero duration. This can be important in
supporting partial-order planning.

@@

    The slave is inserted as an active token in the plan. As such, rules may be activated on the slave, and it may consume resources.
    The token is merged with a matching token already in the plan. Once a slave is merged, the requirement it represents are considered satisfied. The process of merging passes on all restrictions imposed on the slave to the active token upon which it is merged. Merging a token requires finding a target active token that is compatible with the inactive token. For an active token and an inactive token to be compatible requires that they are instances of the same predicate and that no intersections between corresponding variables are empty. The effect of merging is illustrated in Figure 3.

@@

This page has presented the main elements of the EUROPA planning approach. They are:

@@

Timelines as a concise abstraction to express the evolution of state
and behavior for a system component. It provides semantics of mutual
exclusion sequencing in time. Other core abstractions are available in
EUROPA for handling metric resources.

Domain rules to describe internal and external relationships on and
between tokens respectively. Rules are applied to active tokens
(master tokens) referred to as masters and typically produce inactive
tokens (slaves) which are a key vehicle through which the planning
process evolves. The rule structure in EUROPA differs from the more
restrictive commitment to preconditions and effects in classical
planning which prohibits durative actions and disembodied effects
(i.e. effects which may not occur until some temporal distance after
the end of the action).

>>>>

Constraint Satisfaction Programming (also known as Constraint
Programming (CP)) is a discipline that provides a generic framework
for representing, solving and making logical inference on
constraints. A complete treatment of this discipline is given in
\cite{marriott98,apt03} and very concise introductions are provided in
\cite{bartak99,lustig01}.

@@

CP is normally implemented as part of a programming language and
constraints are normally represented as objects \cite{puget95}
\comment{citation}. Any constraint can be introduced and, as long as the
bounds propagation and domain reduction protocols specified by the host
CP system are enforced, it will be indistinguishable from any other
``primitive'' CP constraint, such as $\leq$ or $\geq$. In theory,
solving a CSP problem is NP-Hard \cite{ghallab04}, but often very
efficient in practice using a number of algorithms and techniques that
are well understood.

@@

    An object is an instance of a class. In \eu we model using the
    abstraction of a class to speak about all instances having certain
    properties of state and behavior. In order to describe such state
    and behavior we build on the formalism of first order logic.

@@

A predicate defines a relation between objects and properties. In
\eu, we define such relations between variables whose domains are
sets of objects and sets of properties. For example, we might use a
predicate Pointing(a,p) to indicate that a rover's attitude controller
a is pointing at position p. Note that a is a variable which may have
a number of possible values in a problem with multiple
satellites. Similarly, p is a variable whose values are the set of
possible positions. In a grounded plan, single values will be
specified for each variable as we saw in the case of a solved
Constraint Satisfaction Problem.

In general, is is not sufficient to state that a predicate is true
without giving it some temporal extent over which it holds. Predicates
that are always true can be thought to hold from the beginning to the
end of time. However, in practice, the temporal extent of interest
must be defined with timepoints to represent its start and end. So we
might want to write Pointing(a,s,e,p) to indicate that the attitude
controller a is pointing at position p from time s to time e. In fact,
this pattern of using such predicates to describe both state and
behavior of objects is so prevalent in \eu that we have introduced
a special construct called a Token which has the built in variables to
indicate the object to which the statement principally applies and the
timepoints over which it holds. In \eu, all predicate instances are
Tokens.

@@

Timelines: Often objects in a domain must be described by exactly one
token for every given timepoint in the plan. Such objects are so
common that we provide a special construct in \eu to extend these
semantics to derived classes. Any instances of a class derived from a
Timeline will induce ordering requirements among its tokens in order
to ensure no temporal overlap may occur among them. See below for
further discussion.

Resources: Metric resources, e.g. the energy of a battery or the
capacity of a cargo hold, are objects with an explicit quantitative
state in time and with a circumscribed range of changes that can occur
to impact that state i.e. produce, consume, use, change. These changes
are captured as tokens. Resources are such a common requirement for
\eu users that special constructs are also provided for
them. Instances of classes derived from a Resource will induce
ordering requirements on their Tokens in order to ensure that the
level of the resource remains within specified limits.

@@

It may be sufficient to maintain only a partial-order among
tokens. However, it is often the case that tokens represent states and
actions of a single object in the system. Such tokens are typically
mutually-exclusive. \eu uses a Timeline structure developed in (??)
to concisely capture system components whose behavior is described
over time in this manner.

@@

Figure 1 illustrates how a Timeline can be used to describe the
whereabouts of a tire. The tire is an object in the tire-world
represented as a timeline. It has predicates associated with it which
can describe its states and actions over time. The predicate names
need not contain the tire prefix; this is now implicit since the
tokens are assigned to a specific tire instance (i.e. an instance of a
Timeline). While Timelines are a useful element of the \eu planning
paradigm, they are not essential. A more general notion of a system
Object can be used which does not impose restrictions of
mutual-exclusion or non-zero duration. This can be important in
supporting partial-order planning.

@@

The slave is inserted as an active token in the plan. As such, rules
may be activated on the slave, and it may consume resources.

The token is merged with a matching token already in the plan. Once a
slave is merged, the requirement it represents are considered
satisfied. The process of merging passes on all restrictions imposed
on the slave to the active token upon which it is merged. Merging a
token requires finding a target active token that is compatible with
the inactive token. For an active token and an inactive token to be
compatible requires that they are instances of the same predicate and
that no intersections between corresponding variables are empty. The
effect of merging is illustrated in Figure 3.

@@

This page has presented the main elements of the \eu planning
approach. They are:

@@

Timelines as a concise abstraction to express the evolution of state
and behavior for a system component. It provides semantics of mutual
exclusion sequencing in time. Other core abstractions are available in
\eu for handling metric resources.

Domain rules to describe internal and external relationships on and
between tokens respectively. Rules are applied to active tokens
(master tokens) referred to as masters and typically produce inactive
tokens (slaves) which are a key vehicle through which the planning
process evolves. The rule structure in \eu differs from the more
restrictive commitment to preconditions and effects in classical
planning which prohibits durative actions and disembodied effects
(i.e. effects which may not occur until some temporal distance after
the end of the action).
